---
title: "What are harpsichords missing?"
author: "Y.Cheng"
date: "2/27/2021"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Background of Keyboard Instrument History
Progress in musical style is often accompanied by improvement in the instrument itself. Many believe that the improvement of the harpsichord - a keyboard instrument - to the piano has greatly broadened the expressive power of keyboard music. The prevailing view is that the harpsichord cannot be adjusted for volume, has a single tone, and is so low that in modern times there is no longer a place for the harpsichord except in historical performance and in the performance of certain works with special requirements. This situation brings about another question: how to adapt harpsichord music to a more powerful, more expressive keyboard instrument like the piano?

**Based on the background information about those two instruments, this storyboard aims to showcase how exactly pianists make adaptations to keyboard music that was originally written for harpsichords.**

To take a closer look at  their differences and possible improvements by the piano, we have chosen to play the same piece on both instruments separately. We use the Goldberg Variations, one of the most renowned compositions by J.S. Bach, as a target of analysis, because this series of tunes have been played and recorded on a variety of keyboard instruments including the piano and the harpsichord. 

For corpus, I select two albums about Goldberg Variations, one orchestrated by the piano and the other by the harpsichord. It is important to note that different musicians understand the original music script differently. Consequently, different versions might even deal with repetitions differently, causing great trouble when analyzing them with dynamic warping. That is why I choose two albums with the baseline condition that they share the same repetition pattern.


### Track-level Features: What do we usually expect from a harpsichord track and a piano track?


```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)

harpsichord <- get_playlist_audio_features("", "05gLxIjeqVM12fpJ2738XO")
piano <- get_playlist_audio_features("", "6K7PhwyclS4Lub7BQdEfGn")

awards <-
 bind_rows(
    harpsichord %>% mutate(category = "Harpsichord Version"),
    piano %>% mutate(category = "Piano Version")
  )

#awards %>%
  #ggplot(aes(x = category, y = energy)) +
  #geom_violin()
awards %>%                    # Start with awards.
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) %>%
  ggplot(                     # Set up the plot.
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = mode
    )
  ) +
  geom_point() +              # Scatter plot.
  geom_rug(size = 0.1) +      # Add 'fringes' to show data distribution.
  geom_text(                  # Add text labels from above.
    aes(
      x = valence,
      y = energy,
      label = label
    ),
    data = 
      tibble(
        label = c("", ""),
        category = c("Harpsichord Version", "Piano Version"),
        valence = c(0.090, 0.123),
        energy = c(0.101, 0.967)
      ),
    colour = "black",         # Override colour (not mode here).
    size = 3,                 # Override size (not loudness here).
    hjust = "left",           # Align left side of label with the point.
    vjust = "bottom",         # Align bottom of label with the point.
    nudge_x = -0.05,          # Nudge the label slightly left.
    nudge_y = 0.02            # Nudge the label slightly up.
  ) +
  facet_wrap(~category) +     # Separate charts per playlist.
  scale_x_continuous(         # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   # Use grid-lines for quadrants only.
    minor_breaks = NULL       # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         # Fine-tune the y axis in the same way.
    limits = c(0, 0.55),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        # Use the Color Brewer to choose a palette.
    type = "qual",            # Qualitative set.
    palette = "Paired"        # Name of the palette is 'Paired'.
  ) +
  scale_size_continuous(      # Fine-tune the sizes of each point.
    trans = "exp",            # Use an exp transformation to emphasise loud.
    guide = "none"            # Remove the legend for size.
  ) +
  theme_light() +             # Use a simpler theme.
  labs(                       # Make the titles nice.
    x = "Valence",
    y = "Energy",
    colour = "Mode"
  )
```

*** 

This graph plots valence over energy. It is clearly visible that the harpsichord tracks cuddle in the right uppermost area of the graph, which means most of the harpsichord tracks of Goldberg Variations are identified as "energetic and cheerful" by Spotify, with little variance. The almost non-changing size of the dots symbolize the consistent loudness of harpsichords, just as expected.

On contrary, their piano counterparts show great difference. The variance in terms of both energy and valence is way bigger. There is significant change in loudness, showing great improvement in controlling the volume. 

Probably one of the only shared characteristic between the two versions is the pattern of dots. In both graphs the energy is positively proportional to valence. This is probably due to the restraint style of Goldberg Variations itself.





### Chroma features: How tunings have changed the feeling of music
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```



*** 



### Loudness: Are harpsichords really dumb at volume control?
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```


*** 

Some commentary about Frame 1.


### Timbre features: 
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```

*** 

Some commentary about Frame 1.



### Temporal features: Do harpsichord players do more rubato?
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```

*** 

Some commentary about Frame 1.



### Classification: How differently are harpsichord and piano tracks (of a same score) differently labelled?
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```
*** 

Some commentary about Frame 1.


### Clustering: Exploring the possibility of new insights
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```

*** 

Some commentary about Frame 1.


### Contribution: In summary, what are the differences?