---
title: "What are harpsichords missing?"
author: "Y.Cheng"
date: "2/27/2021"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Background of Keyboard Instrument History
Progress in musical style is often accompanied by improvement in the instrument itself. Many believe that the improvement of the harpsichord - a keyboard instrument - to the piano has greatly broadened the expressive power of keyboard music. The prevailing view is that the harpsichord cannot be adjusted for volume, has a single tone, and is so low that in modern times there is no longer a place for the harpsichord except in historical performance and in the performance of certain works with special requirements.

To take a closer look at  their differences and possible improvements by the piano, we have chosen to play the same piece on both instruments separately. We use the Goldberg Variations by J.S. Bach as a corpus.

### Track-level Features: What do we usually expect from a harpsichord track and a piano track?


```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)

grammy <- get_playlist_audio_features("", "4kQovkgBZTd8h2HCM3fF31")
edison <- get_playlist_audio_features("", "37i9dQZF1DX8mnKbIkppDf")

awards <-
 bind_rows(
    grammy %>% mutate(category = "Grammys"),
    edison %>% mutate(category = "Edisons")
  )

grammy %>% ggplot(aes(x = energy)) + geom_histogram(binwidth = 0.1)
```

*** 

Some commentary about Frame 1.





### Chroma features: How tunings have changed the feeling of music
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```



*** 

Some commentary about Frame 1.



### Loudness: Are harpsichords really dumb at volume control?
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```


*** 

Some commentary about Frame 1.


### Timbre features: 
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```

*** 

Some commentary about Frame 1.



### Temporal features: Do harpsichord players do more rubato?
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```

*** 

Some commentary about Frame 1.



### Classification: How differently are harpsichord and piano tracks (of a same score) differently labelled?
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```
*** 

Some commentary about Frame 1.


### Clustering: Exploring the possibility of new insights
```{r, echo=FALSE}
library(tidyverse)
library(spotifyr)
```

*** 

Some commentary about Frame 1.


### Contribution: In summary, what are the differences?